### 2021-04-16 README.Rmd
Making sure that R CMD CHECK does not have any warnings or errors

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
devtools::load_all()
library(reticulate) # for accessing python objects from r and vice-versa
library(insuranceData) # for the data
library(dplyr) # for the data manipulation
library(purrr)
```

>>>>

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)
devtools::load_all()
library(reticulate) # for accessing python objects from r and vice-versa
library(insuranceData) # for the data
library(dplyr) # for the data manipulation
library(purrr)
```
